\chapter*{ACKNOWLEDGMENTS}
\addcontentsline{toc}{chapter}{ACKNOWLEDGMENTS}
Thanks to my family for the constant support during the writing of this thesis. Thank you for reminding me that there is also life outside the thesis. Without you, the writing of the thesis could have become too intensive from time to time.

Thank you, Antti Leinonen, for providing me with this exciting thesis subject and being my M-Files side supervisor for the project. Thanks also for ensuring sufficient resources and especially time for this thesis. Without your support, the thesis would not most likely exist as it is today.

Thanks for the Hubshare's Arctic Baguette team, especially to Baptiste Tamburini, Corentin Sportiello and Pierre Diancourt for all your support. During the work, you gave me a ton of great comments and feedback related to the work. Thank you also for your technical help during the implementation phase. Thanks also for the rest of the M-Files, Tampere and Lappeenranta colleagues. Thank you for your interest towards the project and for providing great input via interviews and the survey.

Thanks to the university side thesis supervisors Jussi Kasurinen and Erno Vanhala for supervising this thesis project. Your comments during the meetings and review helped refine the thesis to the better shape it stands now.

Thanks to my friends for giving me all kinds of new leads that could be investigated and providing me with interesting new ideas. Thank you also for providing me with many alternative activities outside the thesis.