\chapter{APPENDIX: INTERVIEW QUESTIONS}\label{appendix:interview_questions}
This appendix will present most of the review questions with the interviewee's role information. Some of the questions from the original question set are redacted from this appendix. Omitting is done because some interview questions are irrelevant to this thesis. For example, some questions were related to small technical details of the Hubshare application and were too low-level to be included. In addition to the questions mentioned below, at the end interview, it was asked if there was still something that the interviewee would like to add.

\section{Hubshare interviews}

\subsection*{Hubshare product owner interview}
\begin{itemize}[noitemsep]
	\item How do you see that test automation would help Hubshare?
	\item How do you do prioritisation of the new features?
	\item How test automation cases should be prioritised?
\end{itemize}

\subsection*{Hubshare QA interview}
\begin{itemize}[noitemsep]
	\item What is the status of the Hubshare \gls{qa}?
	\item What are currently the most common Hubshare regressions?
	\item How do you see test automation's role in the Hubshare \gls{qa}?
	\item From your point of view, what are the most crucial aspects from \gls{qa} point of view that should be improved in Hubshare?
\end{itemize}

\subsection*{Hubshare developer}
\begin{itemize}[noitemsep]
	\item How do you feel about test automation?
	\item Could you tell me about Hubshare's daily development?
	\item How are user stories currently developed in Hubshare?
	\item What do you think, which aspects should be taken into account while designing a new test automation system for Hubshare?
\end{itemize}

\section{M-Files test automation interviews}

\subsection*{M-Files senior developer/unit testing expert}
\begin{itemize}[noitemsep]
	\item Could you tell me about the M-Files unit tests?
	\item What is good with the current M-Files unit tests?
	\item What is bad with the current M-Files unit tests?
	\item What would you do differently if the unit testing framework were created now?
	\item How test automation is handled regarding test automation?
\end{itemize}

\subsection*{M-Files integration testing expert}
\begin{itemize}[noitemsep]
	\item Could you tell me about M-Files integration testing?
	\item What is the current workflow regarding M-Files integration testing from different perspectives?
	\item What is good in the current integration tests?
	\item What is bad in the current integration tests?
	\item If the integration tests architecture were created now, what would you do differently?
	\item Is the handling of the bugs visible in the integration tests?
\end{itemize}

\subsection*{M-Files system testing expert}
\begin{itemize}[noitemsep]
	\item What is good in the current M-Files system tests?
	\item What is bad in the current M-Files system tests?
	\item If the M-Files system testing architecture were done, what would you do differently?
\end{itemize}

\subsection*{M-Files testing CI expert}
\begin{itemize}[noitemsep]
	\item Could you tell me about the M-Files test automation deployment?
	\item What is the current workflow regarding test automation from different perspectives?
	\item What kind of code analysis is currently run in the pipeline?
	\item What is the schedule of current \gls{ci} pipelines?
	\item What is good in the current pipeline?
	\item What is bad in the current pipeline?
	\item If the pipeline were created now, what would you do differently?
\end{itemize}

\section{Special interviews}

\subsection*{Agile coach interview}
\begin{itemize}[noitemsep]
	\item How should test automation be included in the agile process?
	\item How to encourage developers to do test automation?
	\item How to tackle with a technical loan?
	\item What do you think about \gls{tdd}?
\end{itemize}