\chapter{CONCLUSIONS}\label{chapter:conclusions}
Even though the introduction of test automation is challenging for the existing project, it is still possible. Extensive research must be done so that the specific application's needs can be adequately understood to achieve good results with the test automation introduction. Like during this study, this activity may include tools like a literature review, interviews and a survey.

In order to form firm management and technical plans, all the gathered information must be evaluated and condensed into clear design documents that clearly state the intents of the new test automation processes and systems. Education and motivation-related matters must be addressed while planning the test automation systems for an existing application. Additionally, it must be ensured that sufficient resources are given for the project. Otherwise, the change process will fail. Technical architecture should be somewhat designed beforehand, but the exacts of the architecture can only be defined during and after the implementation phase. Overall the senses must be kept open during a project to consider all the crucial aspects of the design. All developers must be fully involved with the project from the beginning so that when the new test automation systems are taken into use, they have sufficient knowledge about the tools.

Because this thesis concentrated only on the higher levels of the test automation system, there are still many aspects that could be researched better. For example, education and motivational aspects could be addressed in follow-up research. The thesis could address how test automation education can be organized most effectively and how developers could be adequately motivated to do test automation activities. In addition, especially technical aspects could be researched much more elaborately. Separate theses could even be done for all of the test levels addressed in this thesis. Those follow-up research could go much more deeply into the technical details of the systems and, for example, test more exotic test automation variations. Also, research measuring this project's success over an extended period would be an excellent addition to academic knowledge.